Improving real-time trend estimates using local parametrisation of polynomial regression filters

### 2024-02-12 article_jos.qmd
quote removed

2. Apply symmetric filters to extended forecast series.
This method seems to date back to @deforest1877adjustment, which also suggests modelling a polynomial trend of degree three or less at the end of the period:\
"*As the first $m$ and last $m$ terms of the series cannot be reached directly by the formula, the series should be graphically extended by m terms at both ends, first plotting the observations on paper as ordinates, and then extending the curve along what seems to be its probable course, and measuring the ordinates of the extended portions.*
*It is not necessary that this extension should coincide with what would be the true course of the curve in those parts. *
*The important point is that the m terms thus added, taken together with the $m+1$ adjacent given terms, should follow a curve whose form is approximately algebraic and of a degree not higher than the third.*"\
This is also the approach used in the X-13ARIMA seasonal adjustment method, which extends the series by one year with an ARIMA model.

>>>>

2. Apply symmetric filters to extended forecast series.
This method seems to date back to @deforest1877adjustment, which also suggests modelling a polynomial trend of degree three or less at the end of the period.
This is also the approach used in the X-13ARIMA seasonal adjustment method, which extends the series by one year with an ARIMA model.
